---
title: "Tables"
author: "Paloma"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: 
    toc: true
    toc_float: true
    number_sections: true
    toc_depth: 3
    collapsed: false
    smooth_scroll: true
    theme: "flatly"
    highlight: "tango"
---

```{r libraries, warning = FALSE, message = FALSE, echo = FALSE}
library(rio)
library(dplyr)
library(tidyr)
library(kableExtra)
library(glue)
```

```{r table , warning = FALSE, message = FALSE, echo = FALSE}
source("results_table.R")

```

# Stroke


## Dealing with death in diferent ways

### Stroke. Death as competing event

The observed risk at 15 years is **11.08% **. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_str.sas7bdat")
table(data)
```

### Stroke. Death as lost to follow up

The observed risk at 15 years is **11.08% **. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_str_cens.sas7bdat")
table(data)
```

### Stroke and death combined

The observed risk at 15 years is **37.15%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_str_combined.sas7bdat")
table(data)
```

## Stratified analysis 

### Stroke under 65 years

The observed risk at 15 years is **6.27%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_str65.sas7bdat")
table(data)
```

### Stroke above 65 years and below 80 years

The observed risk at 15 years is **14.53%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_str80.sas7bdat")
table(data)
```

### Stroke in women cohort

The observed risk at 15 years is **9.52 %**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_strw.sas7bdat") 
table(data)
```

### Stroke in men cohort

The observed risk at 15 years is **12.2 %**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_strm.sas7bdat")
table(data)
```

### Stroke in cohort free of hypertension at baseline

The observed risk at 15 years is **6.45 %**. Results with 10 bootstraps.

At the end of study goes to HT use goes to **25%**. SBP goes from 121 to 145.

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_str_healthy.sas7bdat")
table(data)
```
### Stroke in cohort free of heart disease at baseline

The observed risk at 15 years is **10.25%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/stroke/sbp_smoke/results_str_hd.sas7bdat")
table(data)
```

# Dementia

## Dealing with death in diferent ways

### Dementia. Death as competing event

The observed risk at 15 years is **11.08%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_dem.sas7bdat")
table(data)
```


### Dementia. Death as lost to follow up

The observed risk at 15 years is **11.08%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_dem_cens.sas7bdat")
table(data)
```

### Dementia and death combined

The observed risk at 15 years is **37.3%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_dem_combined.sas7bdat")
table(data)
```

## Stratified analysis

### Dementia under 65 years

The observed risk at 15 years is **3.18%**. Results with 5 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_dem65.sas7bdat")
table(data)
```

### Dementia above 65 years and below 80 years

The observed risk at 15 years is **14.36%**. Results with 5 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_dem80.sas7bdat")
table(data)
```

### Dementia in women cohort

The observed risk at 15 years is **10.8%**. Results with 5 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_demw.sas7bdat")
table(data)
```

### Dementia in men cohort

The observed risk at 15 years is **7.13%**. Results with 5 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_demm.sas7bdat")
table(data)
```

### Dementia in cohort free of hypertension at baseline
The observed risk at 15 years is **7.56**. Results with 5 bootstraps.

Up to **25%** at end of study. SPB goes from 121 to 145 mmHg.

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_dem_healthy.sas7bdat")
table(data)
```

### Dementia in cohort free of heart disease at baseline

The observed risk at 15 years is **8.85%**. Results with 5 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/dementia/sbp_smoke/results_dem_hd.sas7bdat")
table(data)
```


# Stroke and Dementia combined

## Dealing with death in diferent ways

### Stroke + Dementia. Death as competing event

The observed risk at 15 years is **18.36%**. Results with 50 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdem.sas7bdat")
table(data)
```

### Stroke + Dementia combined. Death as lost to follow up

The observed risk at 15 years is **12.53**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdem_cens.sas7bdat")
table(data)
```

### Stroke + Dementia + Death. Combined event

The observed risk at 15 years is **41.62%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdem_combined.sas7bdat")
table(data)
```

## Stratified analysis

### Stroke + Dementia under 65 years

The observed risk at 15 years is **8.95**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdem65.sas7bdat")
table(data)
```

### Stroke + Dementia above 65 years and below 80 years

The observed risk at 15 years is **26.53**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdem80.sas7bdat")
table(data)
```

### Stroke + Dementia in women cohort

The observed risk at 15 years is **18.63%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdemw.sas7bdat")
table(data)
```

### Stroke + Dementia in men cohort

The observed risk at 15 years is **18.02%**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdemm.sas7bdat")
table(data)
```

### Stroke + Dementia in cohort free of hypertension at baseline

The observed risk at 15 years is **13.03%**. Results with 10 bootstraps.

SBP goes from 121 to 145.

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdem_healthy.sas7bdat")
table(data)
```

### Stroke + Dementia in cohort free of heart disease at baseline

The observed risk at 15 years is **17.53**. Results with 10 bootstraps

```{r warning= FALSE, echo=FALSE}
data <- import("V:/Uitwissel/Paloma/HT trial/gformula/strdem/sbp_smoke/results_strdem_hd.sas7bdat")
table(data)
```
